\documentclass[12pt]{article} % Set font size to 12 and set document type
\usepackage{geometry}
\geometry{letterpaper, portrait, margin=1in} % Set document layout
\usepackage{graphicx} % Needed to import images
\usepackage{indentfirst} % Enable the first paragraph to be indented
\renewcommand{\familydefault}{\sfdefault} % Set document fonts to sans-serif
\setlength{\parindent}{30pt} % Set indent size

\begin{document}

\begin{flushright}
        WO1 Jik Oh\\
        OOP: dungeon dudes\\
        2023.10.25\\
\end{flushright}

\section*{Project Summary}

Complete the Rogue class according to the provided manual. 
\newline\newline\indent
3 days was given to complete the project.

\section*{Challenges}

This was the first project that used the class repo where everyone was given a maintainer privilege. This could have resulted in a disastorous situation, but everyone was very cautious not to mess it up. In addition, the size of the program was quite overwhelming at first. The Fighter class that was given as an example was such a big help to understand overall design of the program. 

\section*{Successes}

Reading the source code for the Fighter class and matching it against the given manual helped me to understand the overall design of the program. Once I understood the underlying design, writing code for the Rogue class was not too difficult. 

\section*{Lessons Learned}

As a gamer, I felt that this project was the most interesting and fun so far. Even though I did not have time to understand every aspect of the underlying codes, this project definately taught me how multiple packages and modules should be organized and used. 

\end{document}
